ResultsNPS

### 2019-11-21 R/nps_reports/results.Rmd

---
title: "ResultsNPS"
author: "Franco Peschiera"
date: "August 8, 2019"
output:
  html_document: default
  pdf_document: default
params:
  size: get_3_tasks_aggresive_perc_add
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
# setwd('../')
# browser()
source('nps_reports/functions.R')
source('nps_reports/datasets.R')
quant_max <- 0.95
really_small_number <- 0.000001
size <- params$size
df <- do.call(size, args=list())
value_filt_tails <- function(value, each_tail) value %>% between(., quantile(., c(each_tail[1])), quantile(., c(1-each_tail[2])))

scaleFUN <- function(x) sprintf("%.2f", x)

@@

t1_rel <- quality_degr_all %>% filter(experiment=='cuts') %>% use_series(dif_perc)
t1_abs <- quality_degr_all %>% filter(experiment=='cuts') %>% use_series(dif)
quality_degr_quant <- t1_rel %>% quantile()
quality_degr_quant95 <- t1_rel %>% quantile(quant_max)
quality_degr_quant95_abs <- t1_abs %>% quantile(quant_max)

right_tail <- 0.0
quality_degr_all_filt <- 
  quality_degr_all %>% 
  mutate(dif_perc = if_else(dif_perc<= 0, really_small_number, dif_perc)) %>%
  filter(dif_perc %>% value_filt_tails(c(0, right_tail)))

@@

The following boxplot shows the distribution of the gap from the models with respect to the `base` model. Results are shown in logaritmic scale and so we have replace all negative values for a very small one.

```{r}
ggplot(data=quality_degr_all_filt, aes(x=experiment, y=dif_perc)) + theme_minimal() + geom_boxplot() + xlab('Experiment') + ylab('% difference in objective (log2 scale)') + theme(text = element_text(size=20)) + coord_flip() + scale_y_continuous(trans='log2', labels=scaleFUN)

@@

quality_perf <- quality_perf_all %>% filter(experiment=='cuts')
mean_dif <- quality_perf$dif_perc %>%  mean
per_cut <- sum(quality_perf$dif_perc<0)/length(quality_perf$dif_perc)
q95_cut <- quality_perf$dif_perc %>% quantile(0.95)

@@

# this takes some % from each side
each_tail <- 0

@@

The following graph shows the distribution of relative gaps between the best integer solutions found in each of the two models. A negative relative gap means the model outperformed the `base` model in that particular instance. Results are shown in logaritmic scale and so we have replace all negative values for a very small one.

@@

ggplot(data=quality_perf_all_filt, aes(x=experiment, y=dif_perc)) + theme_minimal() + geom_boxplot() + xlab('Experiment') + ylab('% difference in objective (log2 scale)') + theme(text = element_text(size=20)) + coord_flip() + scale_y_continuous(trans='log2', labels=scaleFUN)

@@

Regarding the accomplishment of soft constraints, we can analyze for mutually **optimal solutions**, the quantity of violations in their solutions. For each model and instance, we subtract the `base` model errors. We show only the extra errors (in number) compared to the `base` case.

```{r soft_constraints}
errors_stats <- get_soft_constraints(df, quant_max)
errors_all <- get_soft_constraints_2(df) %>% 
  mutate(dif= if_else(dif<=0, really_small_number, dif))

@@

@@

And the complete distributions in logaritmic scale:

@@

ggplot(data=errors_all, aes(x=experiment, y=dif)) + theme_minimal() + geom_boxplot() + xlab('Experiment') + ylab('absolute difference in errors  (log2 scale)') + theme(text = element_text(size=20)) + coord_flip() + scale_y_continuous(trans='log2', labels=scaleFUN)

@@

```{r variances}
variances_all <- get_variances(df)
# var_per <- variances_all %>% filter(experiment=='cuts') %>% use_series(dif_perc)
# mean_var_reduction <- var_per %>% mean
# quant95_var_reduction <- var_per %>% quantile(quant_max)

@@

variances_all_filt <- 
  variances_all %>% 
  mutate(dif_perc = if_else(dif_perc<= 0, really_small_number, dif_perc))
  # group_by(experiment) %>% 
  # filter(dif_perc %>% value_filt_tails(c(0, right_tail)))

@@

The variance in the frequency of maintenances is a side objective that was not been taken into account previously. The higher the variance, the more difference there is between amount of flight hours between one aircraft and another.
To calculate it, we have, for each fleet type, measured the variance of the distance between maintenances. And we have summed all variances for all fleet types. We do this analysis for all integer solutions obtained.
To better visualize the results, we use a log 2 scale.

@@

ggplot(data=variances_all_filt, aes(x=experiment, y=dif_perc)) + theme_minimal() + geom_boxplot() + xlab('Experiment') + ylab('Difference in variance (in % of base case) (log2 scale)') + theme(text = element_text(size=20)) + coord_flip() + scale_y_continuous(trans='log2', labels=scaleFUN)

>>>>

---
title: "ResultsNPS"
author: "Franco Peschiera"
date: "August 8, 2019"
output:
  html_document: default
  pdf_document: default
params:
  size: get_3_tasks_aggresive_perc_add
  scale: log2
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
# setwd('../')
# browser()
source('nps_reports/functions.R')
source('nps_reports/datasets.R')
default_tail <- 0.05
really_small_number <- 0.000001
size <- params$size
df <- do.call(size, args=list())
value_filt_tails <- function(value, each_tail) value %>% between(., quantile(., c(each_tail[1])), quantile(., c(1-each_tail[2])))

scaleFUN <- function(x) sprintf("%.2f", x)
scale <- params$scale

@@

right_tail <- default_tail
quality_degr_all_filt <- 
  quality_degr_all %>% 
  mutate(dif_perc = if_else(dif_perc<= 0, really_small_number, dif_perc)) %>%
  filter(dif_perc %>% value_filt_tails(c(0, right_tail)))

@@

The following boxplot shows the distribution of the gap from the models with respect to the `base` model. We have replace all negative values for a very small one close to zero. We have taken (`r right_tail*100`\%) values from the right side to better visualize the output.

```{r}
if (scale!='identity'){
  ylab <- sprintf('%% difference in objective (%s scale)', scale)  
} else {
  ylab <- '% difference in objective'
}

ggplot(data=quality_degr_all_filt, aes(x=experiment, y=dif_perc)) + theme_minimal() + geom_boxplot() + xlab('Experiment') + ylab(ylab) + theme(text = element_text(size=20)) + coord_flip() + scale_y_continuous(trans=scale, labels=scaleFUN)

@@

@@

# this takes some % from each side
each_tail <- default_tail

@@

The following graph shows the distribution of relative gaps between the best integer solutions found in each of the two models. A negative relative gap means the model outperformed the `base` model in that particular instance. We have taken (`r each_tail*100`\%) values from each side to better visualize the output.

@@

if (scale!='identity'){
  ylab <- sprintf('%% difference in objective (%s scale)', scale)  
} else {
  ylab <- '% difference in objective'
}

ggplot(data=quality_perf_all_filt, aes(x=experiment, y=dif_perc)) + theme_minimal() + geom_boxplot() + xlab('Experiment') + ylab(ylab) + theme(text = element_text(size=20)) + coord_flip() + scale_y_continuous(trans=scale, labels=scaleFUN)

@@

```{r soft_constraints}
right_tail <- default_tail
errors_stats <- get_soft_constraints(df)
errors_all <- get_soft_constraints_2(df) %>% 
  mutate(dif= if_else(dif<=0, really_small_number, dif))

errors_all_filt <- 
  errors_all %>% 
  filter(dif %>% value_filt_tails(c(0, right_tail)))

@@

Regarding the accomplishment of soft constraints, we can analyze for mutually **optimal solutions**, the quantity of violations in their solutions. For each model and instance, we subtract the `base` model errors. We show only the extra errors (in number) compared to the `base` case. We have taken (`r right_tail*100`\%) values from he right side to better visualize the output.

@@

And the complete distributions:

@@

if (scale!='identity'){
  ylab <- sprintf('absolute difference in errors (%s scale)', scale)
} else {
  ylab <- sprintf('absolute difference in errors')
}

ggplot(data=errors_all_filt, aes(x=experiment, y=dif)) + theme_minimal() + geom_boxplot() + xlab('Experiment') + ylab(ylab) + theme(text = element_text(size=20)) + coord_flip() + scale_y_continuous(trans=scale, labels=scaleFUN)

@@

```{r variances}
variances_all <- get_variances(df)

@@

variances_all_filt <- 
  variances_all %>% 
  group_by(experiment) %>%
  filter(dif_perc %>% value_filt_tails(c(0, right_tail)))

@@

The variance in the frequency of maintenances is a side objective that was not been taken into account previously. The higher the variance, the more difference there is between amount of flight hours between one aircraft and another.
To calculate it, we have, for each fleet type, measured the variance of the distance between maintenances. And we have summed all variances for all fleet types. We do this analysis for all integer solutions obtained.
To better visualize the results, we have taken `r right_tail*100`\% from the right tail.

@@

ggplot(data=variances_all_filt, aes(x=experiment, y=dif_perc)) + theme_minimal() + geom_boxplot() + xlab('Experiment') + ylab('Difference in variance (in % of base case)') + theme(text = element_text(size=20)) + coord_flip()
